---
title: "BST260 - Week 0 Homework"
author: "Gaurav Agarwal"
format: html
editor: visual
execute:
  echo: false
---

Consider $f(x) = ax^2+bx+c=0$. First, we define the variables (default values: $a=1, b=3, c=2$).

```{r}
# User can set values of variables a, b and c
a <- 1
b <- 3
c <- 2
```

Next, we perform the quadratic formula: $x=(-b + sqrt(b^2 - 4*a*c) ) / (2*a)$ to derive the solutions for x. There can be either 0, 1 or 2 roots of x, depending on whether the discriminant ($b^2 - 4*a*c$) is \>0 (2 roots), 0 (1 root) or \<0 (no roots). For the default values:

```{r}
# Define the discriminant
discriminant <- b^2 - 4*a*c

# Determine if the discriminant is >0, 0 or <0 and display the corresponding number of roots of x.
if (discriminant > 0) {
  root1 <- (-b + sqrt(discriminant)) / (2*a)
  root2 <- (-b - sqrt(discriminant)) / (2*a)
  print(paste("Solutions: x = ", root1, " and x = ", root2))
} else if (discriminant == 0) {
  root1 <- -b / (2*a)
  print(paste("Solution: x = ", root1))
} else {
  print("There are no real solutions to this quadratic equation (only complex numbers).")
}

```

The results can be confirmed by plotting the graph of $f(x) = ax^2+bx+c$.

```{r}
x <- seq(-5, 5, length = 300)
plot(x, a*x^2 + b*x + c, type = "l")
abline(h = 0, lty = 2)
```
